Map{R}educe in {MPI} for Large-scale Graph Algorithms

### 2010-03-26 paper/graph.tex
git-svn-id: svn+ssh://software-srn.sandia.gov/svn/mapreduce/trunk@479 3fc257bb-8550-0410-81b3-a5c103da83f7
git-svn-id: svn+ssh://software-srn.sandia.gov/svn/mapreduce/trunk@482 3fc257bb-8550-0410-81b3-a5c103da83f7

\section{Graph Algoriths in MapReduce}

  RMAT generation, pagerank, CC, triangle-finding, Luby, SSSP, other?
  how many variants of something like CC do we want to include?
    I would vote for just one
  discuss possible inefficiency due to a giant CC in CC algorithm

>>>>

\section{Graph Algoriths in MapReduce}
\label{sec:graph}

RMAT generation

pagerank

triangle finding

connected component identification

do wee need differnt variants of CC?

could just do one, discuss possible inefficiency due to giant CC

Luby algorithm for maximally independent sets

SSSP

discuss new optimization in SSSP?
